---
title: "Smokes"
author: "Henry Yang"
format: html
execute:
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.tutorials)
library(tidymodels)
library(broom)
```

```{r}
smokes |> 
  # Group age into 5-year intervals
  mutate(age_bin = 5 * (age %/% 5)) |> 
  # Calculate ever-smoker share by age group and sex
  group_by(age_bin, sex) |> 
  summarize(share = mean(smoke == "Yes"), .groups = "drop") |> 
  # Plot share vs age bin, faceted by sex
  ggplot(aes(x = age_bin, y = share)) +
  geom_point() +
  geom_smooth(method = "loess", formula = y ~ x, se = FALSE) +
  facet_wrap(~ sex) +
  # Format y-axis as percentage
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "Share of Ever-Smokers by Age and Sex",
    x = "Age (5-Year Bins)",
    y = "Share of Ever-Smokers"
  )
```

```{r}
#| cache: true
fit_smokes <- logistic_reg(engine = "glm") |> fit(smoke ~ age + sex, data = smokes)
```

```{r}
library(easystats)
check_predictions(extract_fit_engine(fit_smokes))
```

## Summary
Age and Sex is a strong predictor of being an ever-smoker. This data comes from the 1,000-adult sample from the 2009-2012 NHANES waves, and we are trying to answer  a question: What is the difference in the probability of being an ever-smoker between a 30-year-old woman and a 70-year-old man? One potential weakness in this model is how its data comes from a sample from 2009-2012, almost a decade ago from the population we are actually trying to model.
