---
title: "Smokes"
author: "Henry Yang"
format: html
execute:
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.tutorials)
library(tidymodels)
library(broom)
library(gt)
library(marginaleffects)
```

```{r}
#| cache: true
fit_smokes <- logistic_reg(engine = "glm") |> fit(smoke ~ age + sex, data = smokes)
```

```{r}
plot_predictions(extract_fit_engine(fit_smokes), condition = c("age", "sex"), draw = FALSE) |> 
  ggplot(aes(x = age, y = estimate, color = sex, fill = sex)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "Predicted Probability of Being an Ever-Smoker by Age and Sex",
    subtitle = "Older individuals and men have a higher probability of ever smoking",
    caption = "Data source: NHANES (2009-2012)",
    x = "Age",
    y = "Probability of Ever-Smoking",
    color = "Sex",
    fill = "Sex"
  ) +
  theme_minimal()
```

## Summary
Age and Sex is a strong predictor of being an ever-smoker. This data comes from the 1,000-adult sample from the 2009-2012 NHANES waves, and we are trying to answer  a question: What is the difference in the probability of being an ever-smoker between a 30-year-old woman and a 70-year-old man? One potential weakness in this model is how its data comes from a sample from 2009-2012, almost a decade ago from the population we are actually trying to model. We modeled whether or not an adult is likely to be an ever-smoker as a Bernoulli distribution as a logistic function of age and sex. One quantity of interest is how when comparing two adults of the same age, an adult Male had an average of 54% greater to be an ever-smoker than an adult Female. These estimates might be wrong because of the long gap between the data and the present day. There may be a change in cultural and social traditions in the present day, which might lead to a shift in parameters.
